Race to the Ballot Box: Will Demographics Decide a Winner This Year?

### 2024-10-13 paper/paper.qmd
Updating the paper

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Sameeck Bhatia
  - Sean Chua
thanks: "Code and data are available at: [https://github.com/SameeckBhatia/2024-US-Elections](https://github.com/SameeckBhatia/2024-US-Elections)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

@@

Overview text

@@

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

@@

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

@@

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

@@

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

@@

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

@@

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

@@

Please don't use these as sub-heading labels - change them to be what your point actually is.

@@

@@

Weaknesses and next steps should also be included.

@@

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

>>>>

---
title: "Race to the Ballot Box: Will Demographics Decide a Winner This Year?"
subtitle: "A Regressional Approach to Race and Political Preferences in the 2024 US Elections and Insights on the Next"
author: 
  - Sameeck Bhatia
  - Sean Chua
thanks: "Code and data are available at: [https://github.com/SameeckBhatia/2024-US-Elections](https://github.com/SameeckBhatia/2024-US-Elections)."
date: today
date-format: long
abstract: "Lorem ipsum dolor sit amet, consectetur adipiscing elit. Proin semper lobortis ante quis euismod. Praesent iaculis, nunc sed sagittis dignissim, metus eros venenatis nunc, in posuere risus felis eget nisi. Praesent pulvinar metus velit, sit amet tincidunt dolor consectetur id. Praesent mi nisi, venenatis nec euismod a, vehicula et nisl. In hac habitasse platea dictumst. Sed tristique ligula id suscipit convallis. Donec eget orci in felis consequat fringilla id sit amet lacus."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur tincidunt nec eros ut consequat. Donec consectetur purus non nisl posuere, et gravida erat bibendum. Donec tincidunt tortor suscipit dignissim convallis. Pellentesque elit libero, varius a orci tincidunt, rhoncus sodales augue. Donec egestas, risus vitae feugiat efficitur, nunc velit euismod tellus, at dictum neque orci id nisi. Ut sit amet nisl suscipit, elementum nisl quis, volutpat sem. Phasellus mauris sapien, facilisis at eros eu, consequat gravida lorem. Praesent pulvinar blandit enim sed aliquam. Cras purus nunc, auctor ut lectus sit amet, facilisis dignissim ligula. Cras ligula odio, eleifend sit amet sem ut, sollicitudin imperdiet massa. Vivamus eget mi bibendum, vehicula ipsum a, pretium felis. Maecenas semper vel nisi fringilla luctus.

Donec eleifend tortor eu diam convallis, eu dictum nunc tincidunt. Nunc consectetur sapien arcu, id gravida arcu pulvinar id. Nam dignissim nisl ac ornare maximus. Nullam eget vulputate libero. Vestibulum vitae sapien risus. Vivamus facilisis orci semper, tincidunt massa at, faucibus sem. Ut ac augue elementum, bibendum justo ornare, porta tortor. Vestibulum vitae turpis orci. Sed ultrices ante metus, vel efficitur eros feugiat luctus. Nulla at tincidunt nunc, et dapibus nisi. Proin feugiat, elit pellentesque lobortis pellentesque, magna odio efficitur diam, eget finibus arcu tortor sit amet diam. Duis malesuada lacus sit amet dui auctor pellentesque. Sed fermentum lectus id vulputate euismod. Duis ultrices magna eu leo consequat consectetur. Nulla facilisi.

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur tincidunt nec eros ut consequat. Donec consectetur purus non nisl posuere, et gravida erat bibendum. Donec tincidunt tortor suscipit dignissim convallis. Pellentesque elit libero, varius a orci tincidunt, rhoncus sodales augue. Donec egestas, risus vitae feugiat efficitur, nunc velit euismod tellus, at dictum neque orci id nisi. Ut sit amet nisl suscipit, elementum nisl quis, volutpat sem. Phasellus mauris sapien, facilisis at eros eu, consequat gravida lorem. Praesent pulvinar blandit enim sed aliquam. Cras purus nunc, auctor ut lectus sit amet, facilisis dignissim ligula. Cras ligula odio, eleifend sit amet sem ut, sollicitudin imperdiet massa. Vivamus eget mi bibendum, vehicula ipsum a, pretium felis. Maecenas semper vel nisi fringilla luctus.

Donec eleifend tortor eu diam convallis, eu dictum nunc tincidunt. Nunc consectetur sapien arcu, id gravida arcu pulvinar id. Nam dignissim nisl ac ornare maximus. Nullam eget vulputate libero. Vestibulum vitae sapien risus. Vivamus facilisis orci semper, tincidunt massa at, faucibus sem. Ut ac augue elementum, bibendum justo ornare, porta tortor. Vestibulum vitae turpis orci. Sed ultrices ante metus, vel efficitur eros feugiat luctus. Nulla at tincidunt nunc, et dapibus nisi. Proin feugiat, elit pellentesque lobortis pellentesque, magna odio efficitur diam, eget finibus arcu tortor sit amet diam. Duis malesuada lacus sit amet dui auctor pellentesque. Sed fermentum lectus id vulputate euismod. Duis ultrices magna eu leo consequat consectetur. Nulla facilisi.

@@

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod. Mauris non libero vel ligula tincidunt consequat. Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus. Vivamus feugiat et quam ut consequat. Aenean mollis ullamcorper facilisis. Vivamus scelerisque lectus et elementum vulputate. Nulla et arcu vehicula, iaculis felis sit amet, semper justo. Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem. Curabitur vitae tortor nec ligula scelerisque rutrum. Nullam feugiat odio metus. Cras id convallis ante, ut ornare velit. Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.

@@

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod. Mauris non libero vel ligula tincidunt consequat. Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus. Vivamus feugiat et quam ut consequat. Aenean mollis ullamcorper facilisis. Vivamus scelerisque lectus et elementum vulputate. Nulla et arcu vehicula, iaculis felis sit amet, semper justo. Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem. Curabitur vitae tortor nec ligula scelerisque rutrum. Nullam feugiat odio metus. Cras id convallis ante, ut ornare velit. Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.

@@

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod. Mauris non libero vel ligula tincidunt consequat. Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus. Vivamus feugiat et quam ut consequat. Aenean mollis ullamcorper facilisis. Vivamus scelerisque lectus et elementum vulputate. Nulla et arcu vehicula, iaculis felis sit amet, semper justo. Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem. Curabitur vitae tortor nec ligula scelerisque rutrum. Nullam feugiat odio metus. Cras id convallis ante, ut ornare velit. Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.

@@

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod. Mauris non libero vel ligula tincidunt consequat. Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus. Vivamus feugiat et quam ut consequat. Aenean mollis ullamcorper facilisis. Vivamus scelerisque lectus et elementum vulputate. Nulla et arcu vehicula, iaculis felis sit amet, semper justo. Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem. Curabitur vitae tortor nec ligula scelerisque rutrum. Nullam feugiat odio metus. Cras id convallis ante, ut ornare velit. Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.

@@

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod. Mauris non libero vel ligula tincidunt consequat. Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus. Vivamus feugiat et quam ut consequat. Aenean mollis ullamcorper facilisis. Vivamus scelerisque lectus et elementum vulputate. Nulla et arcu vehicula, iaculis felis sit amet, semper justo. Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem. Curabitur vitae tortor nec ligula scelerisque rutrum.

@@

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod. Mauris non libero vel ligula tincidunt consequat. Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus. Vivamus feugiat et quam ut consequat. Aenean mollis ullamcorper facilisis. Vivamus scelerisque lectus et elementum vulputate. Nulla et arcu vehicula, iaculis felis sit amet, semper justo. Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem. Curabitur vitae tortor nec ligula scelerisque rutrum. Nullam feugiat odio metus. Cras id convallis ante, ut ornare velit. Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.

@@

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod. Mauris non libero vel ligula tincidunt consequat. Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus. Vivamus feugiat et quam ut consequat. Aenean mollis ullamcorper facilisis. Vivamus scelerisque lectus et elementum vulputate. Nulla et arcu vehicula, iaculis felis sit amet, semper justo. Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem. Curabitur vitae tortor nec ligula scelerisque rutrum. Nullam feugiat odio metus. Cras id convallis ante, ut ornare velit. Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod. Mauris non libero vel ligula tincidunt consequat. Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus. Vivamus feugiat et quam ut consequat. Aenean mollis ullamcorper facilisis. Vivamus scelerisque lectus et elementum vulputate. Nulla et arcu vehicula, iaculis felis sit amet, semper justo. Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem. Curabitur vitae tortor nec ligula scelerisque rutrum. Nullam feugiat odio metus. Cras id convallis ante, ut ornare velit. Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.

@@

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod. Mauris non libero vel ligula tincidunt consequat. Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus. Vivamus feugiat et quam ut consequat. Aenean mollis ullamcorper facilisis. Vivamus scelerisque lectus et elementum vulputate. Nulla et arcu vehicula, iaculis felis sit amet, semper justo. Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem. Curabitur vitae tortor nec ligula scelerisque rutrum. Nullam feugiat odio metus. Cras id convallis ante, ut ornare velit. Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.

@@

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod. Mauris non libero vel ligula tincidunt consequat. Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus. Vivamus feugiat et quam ut consequat. Aenean mollis ullamcorper facilisis. Vivamus scelerisque lectus et elementum vulputate. Nulla et arcu vehicula, iaculis felis sit amet, semper justo. Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem. Curabitur vitae tortor nec ligula scelerisque rutrum. Nullam feugiat odio metus. Cras id convallis ante, ut ornare velit. Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.

@@

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod. Mauris non libero vel ligula tincidunt consequat. Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus. Vivamus feugiat et quam ut consequat. Aenean mollis ullamcorper facilisis. Vivamus scelerisque lectus et elementum vulputate. Nulla et arcu vehicula, iaculis felis sit amet, semper justo. Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem. Curabitur vitae tortor nec ligula scelerisque rutrum. Nullam feugiat odio metus. Cras id convallis ante, ut ornare velit. Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.

@@

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod. Mauris non libero vel ligula tincidunt consequat. Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus. Vivamus feugiat et quam ut consequat. Aenean mollis ullamcorper facilisis. Vivamus scelerisque lectus et elementum vulputate. Nulla et arcu vehicula, iaculis felis sit amet, semper justo. Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem. Curabitur vitae tortor nec ligula scelerisque rutrum. Nullam feugiat odio metus. Cras id convallis ante, ut ornare velit. Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.

@@

# Appendix {.unnumbered}
